I cannot imagine that I would have been able to get to this point in my scientific career without the steady flow of encouragement, excitement and support I have received from my advisor, Eric Dufresne.
Over the years he has helped me in more ways than I can hope to describe here.
There is, however, one piece of advice he gave me early on in graduate school that I have found particularly helpful and comforting.
I don't remember his exact phrasing, but the message was, "If you think you know what you're doing, you're doing it wrong."
I found that a particularly elegant and concise description of the real purpose of a Ph.D., to discover information about our universe that is not already known.
Reminding myself that it is OK, even good, to feel lost and confused (at least once in a while) has not only helped in the lab but has become something of a guiding principle in my life.
For this and much more, thank you.

As a member of the Soft Matter Lab I have had the opportunity to work with and learn from some of the smartest, most clever, most fun, and downright nicest people I have had the chance to meet.
Because I do not know with whom I would stop, I am going to thank everyone my time has overlapped with. 
In ways big and small, clear and not clear to me, Vincent Germain, Sara Hashmi, Aric Sanders, Katie Kirkwood, Jacqueline Martinez, Stephen Chapin, Eleanor Millman, Kristina Mois, Elise Novitski, Cecile Mejean, Jason Merrill, Marleen van der Veen, Sunil Sainis, Jin-Gyu Park, Wilfried Engl, Holger Kress, Alla Shundrovsky, Ye Xu, Madeleine Udell, Elissa Dunn, Elizabeth Jerison, Guy German, Alexandra Beautyman, Henry Foote, Aaron Mertz, Ross Boltiyanski, and Raphael Sarfati have all made an impact on me. 
Thanks to all of you.

It would be misleading of me if I didn't explicitly acknowledge the influence of Dr. Jin-Gyu Park.
His dedication and imagination in the lab along with his ability to generate new and interesting particles is astounding and inspiring.
None of the work in my dissertation would have been possible without his willingness to do the impossible --- to teach chemistry to a physicist.
Thank you!

I am grateful to have had the chance to collaborate with many exciting research groups at Yale. 
The groups of Hui Cao, especially Heeso Noh and Seng Fatt Liew, of Corey O'Hern, especially Carl Schreck, and of Richard Prum, especially Vinod Saranathan have been invaluable to my research.
Also, I am grateful for the guidance and scientific advice I have received from Professors Simon Mochrie and Chinedum Osuji.

I have had the good fortune to collaborate with a number of groups and scientists outside of Yale.
Especially important are the relationships I have had with Dr. Lin Yang from the National Synchrotron Light Source at Brookhaven National Labs and with Professor Eric Furst and his student Manish Mittal from the University of Delaware.

The physics faculty and my classmates from the physics department at Illinois Wesleyan University deserve many thanks for providing a great environment for my undergraduate education.
I am particularly appreciative of Professor Gabe Spalding for giving me so much exposure to working in a lab.
It is because of my research experience at Illinois Wesleyan that I was sure graduate school was the best next step for me.

If it weren't for the love and support of my family throughout graduate school and the 21 years before I would not have made it through the experience.
My uncle Fred has been a constant, positive influence in my life and has never been short of good advice.
My brother Andrew has kept me on my toes for as long as I can remember and has always let me know how proud he is.
Most especially I want to thank my parents, Carla and Peter, for simultaneously letting me steer the course of my life and giving me the guidance to not run aground.

Anybody who has been my friend in New Haven has also had the great fortune to be the friend of my fianc\'{e}e, Beezer (known to a few as Elizabeth).
I could not ask for a more loving and supportive partner in my life and I can't thank you enough.
I hope I can be as strong an ally and advocate for you as you have been for me.